---
title: Our Magical Statistics Adventure
author: Barbra and Lisa
date: today
execute:
  fig-device: ragg_png  # This tells R to use a modern, Mac-friendly engine
format: 
  typst: default
  docx: default
  revealjs:
    theme: blood
    transition: fade
    slide-number: true
    css: styles.css
    smaller: true
    scrollable: true
    incremental: false
    output-file: slides.html
---

## Our research questions

Our research topic:

**How do Age, Gender, and Healthcare Encounters relate to Medical Expenses?**

Our sub-topics:

-   How do healthcare expenses vary across age groups?

-   Are there differences in healthcare expenses between male and female patients?

-   Is the number of healthcare encounters associated with healthcare expenses across genders?

```{r}
#| warning: false
#| message: false
#| echo: false
library(targets)
library(gtsummary)
library(gt)
```

## Descriptive Statistics

```{r}
#| label: summary-table
#| echo: false
tar_read(pretty_summary)
```

-   Approximately equal number of males and females

-   Age is balanced between genders

-   Encounters for women are higher

-   Medical expenses for women are higher

## Histogram of Expenses by Age and Gender

```{r}
#| label: age-plot
#| fig-width: 10
#| fig-height: 6
#| echo: false
tar_read(expense_age_plot)
```

-   Even though age and gender were evenly distributed, expenses for women are clearly higher.

-   As age increases, so do expenses for both genders.

## Scatterplot of Encounters to Expenses Compared Between Genders

```{r}
#| label: scatter-plot
#| fig-width: 10
#| fig-height: 6
#| echo: false
tar_read(combined_trend_plot)
```

-   Both genders have increased cost for increased encounters.

-   The increase is steeper for women than men.

## Linear Regression 

```{r}
#| label: regression-output
# Since regression_results is a raw 'lm' object, 
# we use tbl_regression to make it look pretty like the rest!
#| echo: false
library(gtsummary)
tar_read(regression_results) |> 
  tbl_regression()
```

healthcare_expenses \~ age + gender + n_encounters + age\*n_encounters

-   Increasing age leads to increasing expenses

-   Being male decreases expenses

-   Increasing encounters increases expenses

-   Interaction term barely affects slope

All are significant

## Thank you! 💖