---
title: "Our Magical Statistics Adventure"
author: "Barbra and Lisa"
date: today
execute:
  fig-device: ragg_png
format: 
  typst: default
  docx: default
  revealjs:
    theme: blood
    transition: fade
    slide-number: true
    css: styles.css
    smaller: true
    scrollable: true
    incremental: false
    output-file: slides.html
---

## Research Question

We examine how healthcare expenses are associated with patient age, gender, and healthcare utilization, measured as the number of encounters.

Our main research question is:

**How are healthcare expenses associated with age, gender, and healthcare utilization (number of encounters)?**

We also explore three related sub-questions:

-   How do healthcare expenses vary across age groups?
-   Are there differences in healthcare expenses between male and female patients?
-   Is the number of healthcare encounters associated with healthcare expenses across genders?

```{r}
#| warning: false
#| message: false
#| echo: false
library(targets)
library(gtsummary)
library(gt)
```

## Descriptive Statistics

```{r}
#| label: summary-table
#| echo: false
tar_read(pretty_summary)
```

-   Approximately equal number of males and females

-   Age is balanced between genders

-   Encounters for women are higher

-   Medical expenses for women are higher

## Barchart of Expenses by Age and Gender

```{r}
#| label: age-plot
#| fig-width: 10
#| fig-height: 6
#| echo: false
tar_read(expense_age_plot)
```

-   Even though age and gender were evenly distributed, expenses for women are clearly higher.

-   As age increases, so do expenses for both genders.

## Scatterplot of Encounters to Expenses Compared Between Genders

```{r}
#| label: scatter-plot
#| fig-width: 10
#| fig-height: 6
#| echo: false
tar_read(combined_trend_plot)
```

-   Both genders have increased cost for increased encounters.

-   The increase is steeper for women than men.

## Linear Regression

```{r}
#| label: regression-output
# Since regression_results is a raw 'lm' object, 
# we use tbl_regression to make it look pretty like the rest!
#| echo: false
library(gtsummary)
tar_read(regression_results) |> 
  tbl_regression()
```

log(1 + healthcare_expenses) \~ age + gender + n_encounters

-   Increasing age leads to increasing expenses

-   Being male decreases expenses

-   Increasing encounters increases expenses

All are significant

## `Thank you! 💖`